%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Developer CV
% LaTeX Template
% Version 1.0 (28/1/19)
%
% This template originates from:
% http://www.LaTeXTemplates.com
%
% Authors:
% Jan Vorisek (jan@vorisek.me)
% Based on a template by Jan Küster (info@jankuester.com)
% Modified for LaTeX Templates by Vel (vel@LaTeXTemplates.com)
%
% License:
% The MIT License (see included LICENSE file)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[9pt]{developercv} % Default font size, values from 8-12pt are recommended
\usepackage{multicol}

%----------------------------------------------------------------------------------------

\begin{document}

%----------------------------------------------------------------------------------------
%	TITLE AND CONTACT INFORMATION
%----------------------------------------------------------------------------------------

\begin{minipage}[t]{0.45\textwidth} % 45% of the page width for name
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	% If your name is very short, use just one of the lines below
	% If your name is very long, reduce the font size or make the minipage wider and reduce the others proportionately
	\colorbox{black}{{\HUGE\textcolor{white}{\textbf{\MakeUppercase{Sebastiano}}}}} % First name
	
	\colorbox{black}{{\HUGE\textcolor{white}{\textbf{\MakeUppercase{Sanson}}}}} % Last name
	
	\vspace{6pt}
	
	% {\huge Web App Architect} % Career or current job title
\end{minipage}
\begin{minipage}[t]{0.3\textwidth} % 27.5% of the page width for the first row of icons
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	% The first parameter is the FontAwesome icon name, the second is the box size and the third is the text
	% Other icons can be found by referring to fontawesome.pdf (supplied with the template) and using the word after \fa in the command for the icon you want
	% \icon{MapMarker}{12}{Black Mesa East}\\
	\icon{Phone}{12}{+39 342 179 3219}\\
	\icon{At}{12}{\href{mailto:sanson.sebastiano.00@gmail.com}{sanson.sebastiano.00@gmail.com}}\\	
	\icon{Github}{12}{\href{https://github.com/SansonSebastiano}{github.com/SansonSebastiano}}\\
\end{minipage}
% \begin{minipage}[t]{0.275\textwidth} % 27.5% of the page width for the second row of icons
% 	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
% 	% The first parameter is the FontAwesome icon name, the second is the box size and the third is the text
% 	% Other icons can be found by referring to fontawesome.pdf (supplied with the template) and using the word after \fa in the command for the icon you want
% 	% \icon{Globe}{12}{\href{https://alyx.vance.me}{alyx.vance.me}}\\
% 	% \icon{Github}{12}{\href{https://github.com/alyxvance}{github.com/alyxvance}}\\
% 	% \icon{Twitter}{12}{\href{https://twitter.com/@alyxvance}{@alyxvance}}\\
% \end{minipage}

\vspace{0.5cm}

%----------------------------------------------------------------------------------------
%	INTRODUCTION, SKILLS AND TECHNOLOGIES
%----------------------------------------------------------------------------------------

\begin{minipage}[t]{0.4\textwidth} % 40% of the page width for the introduction text
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	\cvsect{Who Am I?}
	Currently pursuing a Master's degree in Computer Science with a specialization in Artificial Intelligence (AI).  Demonstrated passion for AI and IT, actively developing my skills to achieve professional goals in this field. \\
	Outside of academics, I enjoy cooking and expressing my creativity through culinary pursuits.
	% \lorem \lorem \lorem \lorem \lorem\\ % Dummy text
\end{minipage}
\hfill % Whitespace between
\begin{minipage}[t]{0.5\textwidth} % 50% of the page for the skills bar chart
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	\cvsect{Skills}
		\textbf{Languages:} C++, Dart, HTML, SQL, PHP, LaTeX, CSS (beginner), Python (beginner) \\

		\textbf{Technologies:} VSCode, Firebase, GitHub, Git, AMPL (beginner)
\end{minipage}

\vspace{0.5cm}

% \begin{center}
% 	\bubbles{5/VSCode, 3/Firebase, 5/LaTeX, 2/Python, 5/git, 2/AMPL}
% \end{center}

%----------------------------------------------------------------------------------------
%	EXPERIENCE
%----------------------------------------------------------------------------------------

\cvsect{Experience}

\begin{entrylist}
	\entry
		{RiskAPP Srl\\\footnotesize{Conselve, IT}}
		{Mobile developer}
		{06 -- 09/2023}
		{Internship in ICT-oriented professional organisations. \\
		\textbf{Description:} designed and developed the front-end part of a mobile application for the management of the meeting notes using Flutter cross-compiled framework. Conducted requirement analysis, created UI mockups in Figma, used StarUML for UML diagrams and implemented features such as:
		\begin{itemize}
			\item User authentication
			\item Manual/automatic meeting note creation, editing and deletion
			\item Note searching and filtering
		\end{itemize}
		Integrated with the company's back-end system using API REST calls. Implemented an extended version of MVC architectural pattern, to manage the application's complexity and maintainability, and Riverpod library for efficient state management. \\
		Used Git for version control and GitHub for code hosting. \\
 		\texttt{Flutter}\slashsep\texttt{Figma}\slashsep\texttt{StarUML}\slashsep\texttt{GitHub}\slashsep\texttt{VSCode}}
	\entry
		{4pmPrint\\\footnotesize{Portsmouth, UK}}
		{Software developer}
		{06/2019}
		{\textbf{Description:} Design and implementation of a custom print preview system prototype application for a company that provides printing services that enable users to visualize the precise placement and appearance of pre-defined graphics on customizable objects before printing. The application was developed in Java using Eclipse IDE, integrating the MQTT protocol for real-time communication between the client and the server. \\
		This project was developed in a team of 2 people, and we have collaborated to co-designing the application's architecture and the back-end logic, implementing the client-side and server-side components, and testing the application. \\
		Delivered a functional prototype showcasing the system's capabilities to the company.
		\texttt{Java}\slashsep\texttt{Eclipse}\slashsep\texttt{MQTT}}
\end{entrylist}

%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------

\cvsect{Education}

\begin{entrylist}
	\entry
		{University of Padua\\\footnotesize{Padua, IT}}
		{Master's Degree in Computer Science}
		{2023 -- Present}
		{Majoring in Artificial Intelligence}
	\entry
		{University of Padua\\\footnotesize{Padua, IT}}
		{Bachelor's Degree in Computer Science}
		{2020 -- 2023}
		{\textbf{Final grade:} 99/110 \\
		\textbf{Thesis:} "Design and implementation of a mobile application for Meeting Note's management"}
	\entry
		{ITST J.F. Kennedy\\\footnotesize{Pordenone, IT}}
		{Computer Science Higher diploma}
		{2014 -- 2020}
		{\textbf{Diploma grade:} 72/100}
\end{entrylist}

%----------------------------------------------------------------------------------------
%	ADDITIONAL INFORMATION
%----------------------------------------------------------------------------------------

\begin{minipage}[t]{0.3\textwidth}
	\vspace{-\baselineskip} % Required for vertically aligning minipages

	\cvsect{Languages}
	
	\textbf{Italian} - mother tongue \\
	\textbf{English} \\
	- B2 (receptive skills) \\
	- B1 (productive skills)
\end{minipage}
\hfill
\begin{minipage}[t]{0.3\textwidth}
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	\cvsect{Certification}
	
	\textbf{CISCO CCNA} - 2019 \\
	\textbf{CISCO ITE} - 2018	
\end{minipage}

%----------------------------------------------------------------------------------------

\end{document}
